*Prochlorococcus marinus* responses to light and oxygen

### 2024-02-16 Code/Manuscript_O2.Rmd
edited file paths for local versions of oceanprotein figures

```{r set project variables, include = FALSE}
#"..", takes up a level in the directory path
Project <- "PICO"
DataIn <- file.path("..", "Data", "CleanData")
FiguresIn <- file.path("..","Output", "Figures")
FiguresInOceanPro <- file.path( "..", "..", "OceanProteinProchloro", "Output")
FigureInO2Analy <- file.path(  "..", "..", "O2Analyses", "Output")

@@

knitr::include_graphics(file.path(FiguresInOceanPro, "ProchloroPhotosynthDepthO2.png"))
```

@@

knitr::include_graphics(file.path(FiguresInOceanPro, "ProchloroProteinMetabDepthO2.png"))
```

>>>>

```{r set project variables, include = FALSE}
#"..", takes up a level in the directory path
Project <- "PICO"
DataIn <- file.path("..", "Data", "CleanData")
FiguresIn <- file.path("..","Output", "Figures")
FigureInO2Analy <- file.path(  "..", "..", "O2Analyses", "Output")

@@

knitr::include_graphics(file.path(FiguresIn, "ProchloroPhotosynthDepthO2.png"))
```

@@

knitr::include_graphics(file.path(FiguresIn, "ProchloroProteinMetabDepthO2.png"))
```
